Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-23 bbbq_article.tex
Move hypotheses, thanks Geert
Processed feedback, thanks @bogeert

\paragraph{Selection may be detectable in TMHs}

@@

\paragraph{Use of protein data in phylogenetics}

@@

\richel{Will be moved to supplementary materials}

@@

\paragraph{Data sets for TMH epitopes}

To determine the percentages of epitopes overlapping
with TMHs, we use three reference proteomes, which are
a human, viral and bacterial one.
For a human reference proteome, we used the Uniprot human reference proteome
from \url{https://www.uniprot.org/proteomes/UP000005640}), 
which is the same as \cite{bianchi2017}.
The viral reference proteome is represented by
the proteome of the first sequenced SARS-CoV-2 strain (\cite{wu2020new},
GenBank ID of MN908947.3, \url{https://www.ncbi.nlm.nih.gov/nuccore/MN908947})
For bacteria, we used the Uniprot Mycobacterium tuberculosis reference genome
(\url{https://www.uniprot.org/proteomes/UP000001584}) is used.

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    Epitope prediction by EpitopePrediction.
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, SARS-CoV-2 (labeled 'covid') 
    and Mycobacterium tuberculosis (labeled 'myco') proteome,
    Epitope prediction by NetMHCIIpan.
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
  }
  \label{fig:2}
\end{figure}

@@

>>>>

% \paragraph{Selection may be detectable in TMHs}

@@

% \paragraph{Use of protein data in phylogenetics}

@@

@@

% \paragraph{Data sets for TMH epitopes}

To determine the percentages of epitopes overlapping
with TMHs, we use reference proteomes of 
a human, viral and bacterial nature.
For a human reference proteome, we used the Uniprot human reference proteome
from \url{https://www.uniprot.org/proteomes/UP000005640}), 
which is the same as used previously (\cite{bianchi2017}).
The viral reference proteome is represented by
the proteome of the first sequenced SARS-CoV-2 strain (\cite{wu2020new},
GenBank ID of MN908947.3, \url{https://www.ncbi.nlm.nih.gov/nuccore/MN908947})
For bacteria, we used the Uniprot Mycobacterium tuberculosis reference genome
(\url{https://www.uniprot.org/proteomes/UP000001584}) is used.

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
    \richel{Epitope prediction by EpitopePrediction.}.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    Percentage of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    \richel{Epitope prediction by NetMHCIIpan.}
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:2}
\end{figure}

@@

\richel{As a reminder, to focus the research on}
